SDR enhancement by clouds

### 2024-04-01 article/article.Rmd
Commit 2024-03-28 10:14
Commit 2024-04-01 12:14

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.
.... cite ....
The variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment.
.... cite ....
A big aspect of this variability are the interaction with the clouds. In general
clouds, absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance [see references therein].
.... cite ....
Those enhancements have been reported to be able to exceed .... and duration.
.... cite ....
@Martins2022

@@

<!-- our work -->
In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

@@

<!-- Libradtran options -->
For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a
"pseudospherical" geometry and the "LOWTRAN" gas parameterization. For each
combination of conditions we use a SZA step of $0.2^\circ$.
<!-- Atmospheric options -->
For the atmospheric characteristics, we iterated for combinations of AOD at
$500\,\text{nm}$ ($t_{500\text{nm}}$) with additional offsets of $\pm1$ and
$\pm2\sigma$, and water column ($w_h$), also with offsets of $\pm1$ and $\pm2\sigma$.
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
(afglms) and the "AFG Latmospheric constituent profile, midlatitude winter" (afglmw)
[@Anderson1986].

<!-- Lookup table -->
To create a look up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral, to the one of the total solar irradiance (TSI)
provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site.  With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

<!-- reasoning for cretria -->
We have to note, that the differentiation of the threshold factor was needed, because
of the high irradiance values we observed, early in the morning and late on the
afternoon. We have confirmed, by inspecting images from the sky cam, that we have
duration of elevated irradiance, either due the clearness of the atmosphere, or some
interferences by reflections on nearby bright surfaces. Although, these cases may
mask some of the CE events. The actual CE events, produce higher irradiance and thus
are identified as such. As a side effect, the reported OIR will be slight
underestimated for those SZAs, but the overall contribution of those cases to the
total daily energy, is minimal due the low occurrences and the lower irradiances.

@@

These selections has some subjectivity, as the definition of clear sky, is depended
on the intended usage. Our main focus is to be able to identify the OIR created by the
clouds. Although, the aerosols and water vapor are always present and can not be
completely removed. 
The effect of the different clearness levels

@@

- Include Example of days plot in the Appendix?
... this is more clear to understand and describe ....

@@

The distribution of the CE over irradiance spreads uniformly
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
between the events frequency and events intensity. This is expected as, the stronger
the CE events become, the more rare are the particular atmospheric and sun conditions
to occur.

>>>>

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
[@Gray2010].  It has direct practical application, in different industries, like
energy production and agriculture method.  The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research focus on predicting the renewable energy production in a  very fine
timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance [see references therein].
.... cite ....
Those enhancements have been reported to be able to exceed .... and duration.
And in extreme cases can compromise the integrity of the infrastructure.
.... cite ....
@Martins2022

@@

<!-- our work -->
In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty-year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

@@

<!-- Libradtran options -->
For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a
"pseudospherical" geometry and the "LOWTRAN" gas parameterization. For each
combination of conditions we use a SZA step of $0.2^\circ$.
<!-- Atmospheric options -->
For the atmospheric characteristics, we iterated for combinations of AOD at
$500\,\text{nm}$ ($t_{500\text{nm}}$) with additional offsets of $\pm1$ and
$\pm2\sigma$, and water column ($w_h$), also with offsets of $\pm1$ and $\pm2\sigma$.
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
(afglms) and the "AFGL atmospheric constituent profile, midlatitude winter" (afglmw)
[@Anderson1986].

<!-- Lookup table -->
To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral, to the one of the total solar irradiance (TSI)
provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site.  With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

<!-- reasoning for cretria -->
We have to note, that the differentiation of the threshold factor was needed, because
of the high irradiance values we observed, early in the morning and late in the
afternoon. We have confirmed, by inspecting images from the sky cam, that we have
duration of elevated irradiance, either due to the clearness of the atmosphere, or some
interferences by reflections on nearby bright surfaces. Although, these cases may
mask some of the CE events. The actual CE events, produce higher irradiance and thus
are identified as such. As a side effect, the reported OIR will be slight
underestimated for those SZAs, but the overall contribution of those cases to the
total daily energy, is minimal due the low occurrences and the lower irradiances.

@@

These selections have some subjectivity, as the definition of clear sky, is depended
on the intended usage. Our main focus is to be able to identify the OIR created by the
clouds. Although, the aerosols and water vapor are always present and can not be
completely removed. 
The effect of the different clearness levels

@@

- Include Example of days plot in the Appendix?
... this is clearer to understand and describe ....

@@

The distribution of the CE over irradiance spreads uniformly
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
between the events frequency and events intensity. This is expected as, the stronger
the CE events become, the rarer the particular atmospheric and sun conditions
occur.

### 2024-04-01 article/article.tex
Commit 2024-03-28 10:14
Commit 2024-04-01 12:14

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-27}

@@

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.
\ldots. cite \ldots.
The variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment.
\ldots. cite \ldots.
A big aspect of this variability are the interaction with the clouds. In general
clouds, absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance {[}see references therein{]}.
\ldots. cite \ldots.
Those enhancements have been reported to be able to exceed \ldots. and duration.
\ldots. cite \ldots.
Martins, Mantelli, and Rüther (2022)

@@

In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

@@

For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a
``pseudospherical'' geometry and the ``LOWTRAN'' gas parameterization. For each
combination of conditions we use a SZA step of \(0.2^\circ\).
For the atmospheric characteristics, we iterated for combinations of AOD at
\(500\,\text{nm}\) (\(t_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
\(\pm2\sigma\), and water column (\(w_h\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
(afglms) and the ``AFG Latmospheric constituent profile, midlatitude winter'' (afglmw)
(Anderson et al. 1986).

To create a look up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral, to the one of the total solar irradiance (TSI)
provided by NOAA (Coddington et al. 2005). Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements. For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw). Finally, we calculated
the clear sky irradiance value at the horizontal plane. Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site. With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

We have to note, that the differentiation of the threshold factor was needed, because
of the high irradiance values we observed, early in the morning and late on the
afternoon. We have confirmed, by inspecting images from the sky cam, that we have
duration of elevated irradiance, either due the clearness of the atmosphere, or some
interferences by reflections on nearby bright surfaces. Although, these cases may
mask some of the CE events. The actual CE events, produce higher irradiance and thus
are identified as such. As a side effect, the reported OIR will be slight
underestimated for those SZAs, but the overall contribution of those cases to the
total daily energy, is minimal due the low occurrences and the lower irradiances.

@@

\begin{itemize}
\tightlist
\item
  Include Example of days plot in the Appendix?
  \ldots{} this is more clear to understand and describe \ldots.
\end{itemize}

@@

@@

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-04-01}

@@

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
(Gray et al. 2010). It has direct practical application, in different industries, like
energy production and agriculture method. The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research focus on predicting the renewable energy production in a very fine
timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance {[}see references therein{]}.
\ldots. cite \ldots.
Those enhancements have been reported to be able to exceed \ldots. and duration.
And in extreme cases can compromise the integrity of the infrastructure.
\ldots. cite \ldots.
Martins, Mantelli, and Rüther (2022)

@@

In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty-year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

@@

For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a
``pseudospherical'' geometry and the ``LOWTRAN'' gas parameterization. For each
combination of conditions we use a SZA step of \(0.2^\circ\).
For the atmospheric characteristics, we iterated for combinations of AOD at
\(500\,\text{nm}\) (\(t_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
\(\pm2\sigma\), and water column (\(w_h\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
(afglms) and the ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
(Anderson et al. 1986).

To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral, to the one of the total solar irradiance (TSI)
provided by NOAA (Coddington et al. 2005). Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements. For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw). Finally, we calculated
the clear sky irradiance value at the horizontal plane. Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site. With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

We have to note, that the differentiation of the threshold factor was needed, because
of the high irradiance values we observed, early in the morning and late in the
afternoon. We have confirmed, by inspecting images from the sky cam, that we have
duration of elevated irradiance, either due to the clearness of the atmosphere, or some
interferences by reflections on nearby bright surfaces. Although, these cases may
mask some of the CE events. The actual CE events, produce higher irradiance and thus
are identified as such. As a side effect, the reported OIR will be slight
underestimated for those SZAs, but the overall contribution of those cases to the
total daily energy, is minimal due the low occurrences and the lower irradiances.

@@

\begin{itemize}
\tightlist
\item
  Include Example of days plot in the Appendix?
  \ldots{} this is clearer to understand and describe \ldots.
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Graabak2016}{}}%
Graabak, Ingeborg, and Magnus Korpås. 2016. {``Variability Characteristics of European Wind and Solar Power Resources---a Review.''} \emph{Energies} 9 (6): 449. \url{https://doi.org/10.3390/en9060449}.

\leavevmode\vadjust pre{\hypertarget{ref-Gray2010}{}}%
Gray, L. J., J. Beer, M. Geller, J. D. Haigh, M. Lockwood, K. Matthes, U. Cubasch, et al. 2010. {``{SOLAR} {INFLUENCES} {ON} {CLIMATE}.''} \emph{Reviews of Geophysics} 48 (4): RG4001. \url{https://doi.org/10.1029/2009RG000282}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Inman2013}{}}%
Inman, Rich H., Hugo T. C. Pedro, and Carlos F. M. Coimbra. 2013. {``Solar Forecasting Methods for Renewable Energy Integration.''} \emph{Progress in Energy and Combustion Science} 39 (6): 535--76. \url{https://doi.org/10.1016/j.pecs.2013.06.002}.
